\bf Manifold Clustering in the Generalized Random Dot Product Graph

### 2022-04-24 draft/draft.Rmd
still cleaning up proofs of theorems 2 and 3

\begin{theorem}[Community detection for one-dimensional nonintersecting manifolds with noise]
\label{nonintersect-with-noise}
Suppose the same setup as in Theorem \ref{nonintersect-no-noise}. 
Define $y_i = x_i + e_i$ and $B_n$ as the event such that $\|y_{(i+1)}^{(k)} - y_{(i)}^{(k)}\| > \|y_{(i)}^{(k)} - y_{(j)}^{(\ell)}\|$ for some $i$, $j$, $k$, and $\ell$. 
Then if $\max_i \|e_i\| < \delta / 3$, for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, $P(B_n) < \epsilon$. 
\end{theorem}

\begin{theorem}[Community detection for one-dimensional nonintersecting manifold block models]
\label{nonintersect-mbm}
Suppose we have the same setup as in Theorem \ref{nonintersect-no-noise}. 
Let $p, q \geq 0$ such that $p + q = d$ where $d$ is the dimension of the range of each $g_k$. 
Suppose we draw $A \sim \GRDPG_{p,q}(X; \rho_n)$ for some sparsity parameter $\rho_n \in (0, 1]$, and let $\hat{X}$ be the ASE of $A$. 
Then for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, single linkage clustering produces zero community detection error with probability 1. 
\end{theorem}

@@

This converges to $1$ in the limit $n \to \infty$.
\end{proof}

\begin{proof}[Proof of Theorem \ref{nonintersect-no-noise}]
For this theorem to be true, there are two additional conditions: 
First, each $n_k \to \infty$ as $n \to \infty$, or the sample size on each manifold grows with $n$, and second, the number of manifolds $K$ remains fixed. 
Then this is a direct consequence of Lemma \ref{lem:lim-d}. 
Here, we denote $m = \min_k n_k$ as the sample size of the manifold with the fewest points.

@@

Here, we extend the results on the line to the unit hypercube. The following theorem is based on Lemma 2 of \citet{trosset2020rehabilitating}.

>>>>

\begin{theorem}[Community detection for one-dimensional nonintersecting manifolds with noise]
\label{nonintersect-with-noise}
Suppose the same setup as in theorem \ref{nonintersect-no-noise}. 
Define $y_i = x_i + e_i$ and $B_n$ as the event such that $\|y_{(i+1)}^{(k)} - y_{(i)}^{(k)}\| > \|y_{(i)}^{(k)} - y_{(j)}^{(\ell)}\|$ for some $i$, $j$, $k$, and $\ell$. 
Then if $\max_i \|e_i\| < \delta / 3$, for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, $P(B_n) < \epsilon$. 
\end{theorem}

\begin{theorem}[Community detection for one-dimensional nonintersecting manifold block models]
\label{nonintersect-mbm}
Suppose we have the same setup as in theorem \ref{nonintersect-no-noise}. 
Let $p, q \geq 0$ such that $p + q = d$ where $d$ is the dimension of the range of each $g_k$. 
Suppose we draw $A \sim \GRDPG_{p,q}(X; \rho_n)$ for some sparsity parameter $\rho_n \in (0, 1]$, and let $\hat{X}$ be the ASE of $A$. 
Then for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, single linkage clustering produces zero community detection error with probability 1. 
\end{theorem}

@@

Since $(1 - a \delta) < 1$ and $(1 - F(1-\delta) - a \delta) < 1$, this converges to $1$ in the limit $n \to \infty$. 
Then for any $\epsilon \in (0, 1)$, we can always solve for an $n$ such that $1 - (n-1) (1 - a \delta)^n (n-1) (1 - F(1 - \delta) - a \delta)^n \geq 1 - \epsilon$ holds. 
\end{proof}

\begin{proof}[Proof of theorem \ref{nonintersect-no-noise}]
This theorem requires two additional conditions: 
First, each $n_k \to \infty$ as $n \to \infty$, and second, the number of manifolds $K$ remains fixed. 
These are satisified by the model assumptions. 
Then this is a direct consequence of Lemma \ref{lem:lim-d}. 
Denoting $m = \min_k n_k$ as the sample size of the manifold with the fewest points,

@@

\begin{proof}[Proof of theorem \ref{nonintersect-with-noise}]
\end{proof}

\begin{proof}[Proof of theorem \ref{nonintersect-mbm}]
\end{proof}

Here, we extend the results on the line to the unit hypercube. The following lemma is based on lemma 2 of \citet{trosset2020rehabilitating}.

### 2022-04-24 draft/draft.tex
still cleaning up proofs of theorems 2 and 3

\begin{theorem}[Community detection for one-dimensional nonintersecting manifolds with noise]
\label{nonintersect-with-noise}
Suppose the same setup as in Theorem \ref{nonintersect-no-noise}. 
Define $y_i = x_i + e_i$ and $B_n$ as the event such that $\|y_{(i+1)}^{(k)} - y_{(i)}^{(k)}\| > \|y_{(i)}^{(k)} - y_{(j)}^{(\ell)}\|$ for some $i$, $j$, $k$, and $\ell$. 
Then if $\max_i \|e_i\| < \delta / 3$, for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, $P(B_n) < \epsilon$. 
\end{theorem}

\begin{theorem}[Community detection for one-dimensional nonintersecting manifold block models]
\label{nonintersect-mbm}
Suppose we have the same setup as in Theorem \ref{nonintersect-no-noise}. 
Let $p, q \geq 0$ such that $p + q = d$ where $d$ is the dimension of the range of each $g_k$. 
Suppose we draw $A \sim \mathrm{GRDPG}_{p,q}(X; \rho_n)$ for some sparsity parameter $\rho_n \in (0, 1]$, and let $\hat{X}$ be the ASE of $A$. 
Then for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, single linkage clustering produces zero community detection error with probability 1. 
\end{theorem}

>>>>

\begin{theorem}[Community detection for one-dimensional nonintersecting manifolds with noise]
\label{nonintersect-with-noise}
Suppose the same setup as in theorem \ref{nonintersect-no-noise}. 
Define $y_i = x_i + e_i$ and $B_n$ as the event such that $\|y_{(i+1)}^{(k)} - y_{(i)}^{(k)}\| > \|y_{(i)}^{(k)} - y_{(j)}^{(\ell)}\|$ for some $i$, $j$, $k$, and $\ell$. 
Then if $\max_i \|e_i\| < \delta / 3$, for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, $P(B_n) < \epsilon$. 
\end{theorem}

\begin{theorem}[Community detection for one-dimensional nonintersecting manifold block models]
\label{nonintersect-mbm}
Suppose we have the same setup as in theorem \ref{nonintersect-no-noise}. 
Let $p, q \geq 0$ such that $p + q = d$ where $d$ is the dimension of the range of each $g_k$. 
Suppose we draw $A \sim \mathrm{GRDPG}_{p,q}(X; \rho_n)$ for some sparsity parameter $\rho_n \in (0, 1]$, and let $\hat{X}$ be the ASE of $A$. 
Then for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, single linkage clustering produces zero community detection error with probability 1. 
\end{theorem}
